---
title: "Terrestrial_data_example"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
renv::restore()
library(neonUtilities)
library(neonstore)
library(tidyverse)
library(lubridate)
library(contentid)
```

Load Flux data

```{r}
# Terrestrial
#DP4.00200.001 & DP1.00094.001
neon_store(product = "DP4.00200.001", n = 500) 
flux_data <- neon_table(table = "nsae-basic")

flux_data <- flux_data %>% 
  mutate(time = as_datetime(timeBgn))

```

## CO2 flux data (turblent + storage flux)

Requires both the turbulent and storage flux to pass the QAQC

```{r}
flux_data %>% filter(qfqm.fluxCo2.turb.qfFinl == 0 & 
                     qfqm.fluxCo2.stor.qfFinl == 0) %>% 
  ggplot(aes(x = time, y = data.fluxCo2.nsae.flux)) + 
  geom_point() +
  scale_x_datetime(date_labels = "%Y-%m") +
  facet_wrap(~siteID)
```

## Latent flux data (turblent + storage flux)

Requires both the turbulent and storage flux to pass the QAQC


```{r}
flux_data %>% filter(qfqm.fluxH2o.turb.qfFinl == 0 & 
                    qfqm.fluxH2o.stor.qfFinl == 0) %>% 
  ggplot(aes(x = time, y = data.fluxH2o.nsae.flux)) + 
  geom_point() +
  scale_x_datetime(date_labels = "%Y-%m") +
  facet_wrap(~siteID)
```

# What if we only use turblent fluxes

Requires only turbulent pass the QAQC

```{r}
flux_data %>% filter(qfqm.fluxCo2.turb.qfFinl == 0) %>% 
  ggplot(aes(x = time, y = data.fluxCo2.turb.flux)) + 
  geom_point() +
  scale_x_datetime(date_labels = "%Y-%m") +
  facet_wrap(~siteID)
```



## Soil moisture

Load data

```{r}
neon_store(table = "SWS_30_minute", n = 500) 
d2 <- neon_read(table = "sensor_positions") 
sm30 <- neon_table(table = "SWS_30_minute")
sensor_positions <- neon_table(table = "sensor_positions")
```

Clean up sensor positions

```{r}
sensor_positions <- sensor_positions %>% 
  mutate(horizontalPosition = str_sub(sensor_positions$HOR.VER, 1, 3),
         verticalPosition = str_sub(HOR.VER, 5, 7),
         siteID = str_sub(file, 10, 13)) %>% 
  rename(sensorDepths = zOffset) %>% 
  filter(siteID %in% c("KONZ", "BART", "OSBS", "SRER")) %>% 
  select(sensorDepths, horizontalPosition, verticalPosition, siteID)

sm30 <- left_join(sm30, sensor_positions, by = c("siteID", "verticalPosition", "horizontalPosition"))
```
  
Clean soil moisture with QC flag

```{r}
sm30 <- sm30 %>% 
  select(startDateTime, endDateTime, VSWCMean, siteID, horizontalPosition, verticalPosition, VSWCFinalQF, sensorDepths) %>% 
  mutate(VSWCMean = as.numeric(VSWCMean)) %>% 
  filter(VSWCFinalQF == 0)
```

### BART

Panels are depth

```{r}
sm30 %>% filter(siteID == "BART" & horizontalPosition == "001") %>% 
  ggplot(aes(x = startDateTime, y = VSWCMean)) +
  geom_point() +
  facet_wrap(~sensorDepths)
```

### KONZ

```{r}
sm30 %>% filter(siteID == "KONZ" & horizontalPosition == "001") %>% 
  ggplot(aes(x = startDateTime, y = VSWCMean)) +
  geom_point()+
  facet_wrap(~factor(sensorDepths))
```

### OSBS

```{r}
sm30 %>% filter(siteID == "OSBS" & horizontalPosition == "001") %>% 
  ggplot(aes(x = startDateTime, y = VSWCMean)) +
  geom_point()+
  facet_wrap(~factor(sensorDepths))
```

### SRER

```{r}
sm30 %>% filter(siteID == "SRER" & horizontalPosition == "001") %>% 
  ggplot(aes(x = startDateTime, y = VSWCMean)) +
  geom_point()+
  facet_wrap(~factor(sensorDepths))
```
